Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-05 p2/rec-sound.tex
Simpler lemma

\noindent
We would like to prove that $\worksmbb{A,B}{B\cc \reca}$.
From the above we know that we can move commands in $\acbnp$
to the beginning of $B$ and so this is equivalent to
\[ \worksmbb{A,B}{\acb\cc \bma\cc \reca}. \]
As we already know that $\reca\indep\bma$
and that $\worksmbb{A,B}{\acb\cc \bma}$
(as $\worksmbb{A,B}{B}$),
we can prove our theorem based on \cref{indep_prefix_combine}
if we can prove that
\[ \worksmbb{A,B}{\acb\cc \reca}. \]
Based on \cref{r_invmove} and \cref{repr_works_is_same}, and because
we already know that $\worksmbb{A,B}{\acbnp}$,
this is equivalent to
\[ \worksmbb{\acbi\cc A\T,\acbi\cc B\T}{\reca\T}. \]

To restate some results above, we therefore already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
because of \cref{r_invmove}
as $\worksmbb{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
\end{itemize}

>>>>

\noindent
We would like to prove that $\worksmbb{A,B}{B\cc \reca}$.
From the above we know that we can move commands in $\acbnp$
to the beginning of $B$ and so this is equivalent to
\[ \worksmbb{A,B}{\acb\cc \bma\cc \reca}. \]
We can prove this if we can show that
\[ \worksmbb{A,B}{\acb\cc \reca}. \]
This is because we already know
that $\worksmbb{A,B}{\acb\cc \bma}$ (as $\worksmbb{A,B}{B}$),
which, combined with the above, yields
\[ \worksmbb{A,B}{\acb\cc \reca, \acb\cc \bma}. \]
Also, as $\reca\indep\bma$,
from \cref{indep_prefix_combine}
we know
\[ \worksmbb{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
As $\worksmeqsign$ is transitive, combining the two results
gives the statement we intended to prove.

To restate some results above, we therefore already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
% TODO Inverse is used here - how/why?
\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
because of \cref{r_invmove}
as $\worksmbb{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
\end{itemize}

### 2017-10-05 p2/works-inverse.tex
New section title
Simpler lemma

\subsection{Conditional Operation and Inverse Sequences}

@@

As the types of values determine whether a command breaks a filesystem,
we know $\Dom{A}=\Dom{A\T}$ and therefore $\Dom{\sqs{A}}=\Dom{\sqs{A}\T}$.
From this it follows that

@@

\begin{mylem}\label{indep_prefix_combine}
The combination of two sequences with a common head and independent tails 
is defined wherever the two sequences are defined:
\begin{gather*}
 \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
 \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
\end{gather*}
\end{mylem}
\begin{proof}
Based on \cref{repr_works_is_same} we have
$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
and from \cref{r_invmove} we know
$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
Using \cref{combine_independent_sequences} we get
$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
and chaining these (as $\worksmeqsign$ is transitive)
we get
$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.

From $\worksmxb{\sqs{S}}{A\cc B}$ we also know $\worksmxb{\sqs{S}}{A}$ and $\worksmxb{\sqs{S}\T}{A\T}$.
We can combine this and $\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$ using
\cref{r_invmove} to get
$\worksmxb{\sqs{S}\T}{A\T\cc B\T\cc C\T}$, and from \cref{repr_works_is_same} we know
$\worksmxb{\sqs{S}}{A\cc B\cc C}$.
\end{proof}

>>>>

\subsection{Domains and Inverse Sequences}

@@

As the types of values determine whether a command breaks a filesystem,
we know $\Dom{A}=\Dom{A\T}$ and therefore $\Dom{\sqs{A}}=\Dom{\sqs{A}\T}$.
From this it follows that
% TODO what's the set of all filesystems?

@@

\begin{mylem}\label{indep_prefix_combine}
The combination of two sequences with a common head and independent tails 
is defined wherever the two sequences are defined:
\[ B\indep C \Rightarrow \worksmbb{A\cc B, A\cc C}{A\cc B\cc C} \]
\end{mylem}
\begin{proof}
This is trivial unless $\worksmnil{A}$, so we assume that that is the case.
From $B\indep C$ and \cref{combine_independent_sequences} we know
$\worksmbb{B, C}{B\cc C}$.
Based on \cref{repr_works_is_same} this is equivalent to
$\worksmbb{B\T, C\T}{B\T\cc C\T}$.
Since $A\T^{-1}\cc A\T \equiv \emptyseq$, this can also be written as
\[\worksmxb{A\T^{-1}\cc\{A\T\cc B\T, A\T\cc C\T\}}{B\T\cc C\T}.\]
From \cref{worksextpostfix} we also know that
$\worksmbb{A\T\cc B\T, A\T\cc C\T}{A\T}$.
Combining the last two statements using \cref{r_invmove}
we get
\[ \worksmbb{A\T\cc B\T, A\T\cc C\T}{A\T\cc B\T\cc C\T}, \]
which with \cref{repr_works_is_same} proves the
\namecref{indep_prefix_combine}.
\end{proof}
